Detection and Classification of Supernova Gravitational Waves Signals: A Deep Learning Approach

### 2020-04-17 main.tex
comments incorporated, samples increased to 1.08e6

%
% the TAP as a function of distance
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:eff1}
            \includegraphics[width=0.475\textwidth]{Neutrino_efficiency.png}
        }\quad
        \subfigure[]{
            \label{fig:eff2}
            \includegraphics[width=0.475\textwidth]{Magnetarotational_efficiency.png}
        }
    \end{center}
    \caption{Efficiency curves showing the classification ability of the
\ac{CNN} as a function of distance for both mechanisms and networks.  The left
panel shows the results for the neutrino-driven mechanism, while the right
shows those for the magnetorotational mechanism. In both panels, the solid
lines show the results for the network H+L+VK, and the dashed lines for HLVK.
Three \acp{FAP} values are chosen, blue for \ac{FAP} $=1\%$, green for \ac{FAP}
$=0.1\%$, red for \ac{FAP} $=0.01\%$.\label{fig:eff}}
\end{figure*}

%
% the TAP vs distance plot for fixed threshold
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:ROCfixed1}
            \includegraphics[width=0.475\textwidth]{ROC_fixed_neutrino.png}
        }\quad
        \subfigure[]{
            \label{fig:ROCfixed2}
            \includegraphics[width=0.475\textwidth]{ROC_fixed_mag.png}
        }
    \end{center}
    \caption{Efficiency curves showing the ability of the \ac{CNN} in
distinguishing input data with a fixed decision threshold $(50\%)$, 
and their corresponding \acp{FAP} and \ac{TAP}. 
The left panel shows the results for the neutrino-driven mechanism, and
the right shows that for the magnetorotational mechanism. In both panels, the
solid lines show the \acp{TAP} and \acp{FAP} for the network H+L+VK, and the
dashed lines show those for HLVK.\label{fig:ROCfixed}}
\end{figure*}

>>>>

%
% the TAP as a function of distance
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:eff1}
            \includegraphics[width=0.475\textwidth]{Neutrino_efficiency.png}
        }\quad
        \subfigure[]{
            \label{fig:eff2}
            \includegraphics[width=0.475\textwidth]{Magnetarotational_efficiency.png}
        }
    \end{center}
    \caption{Efficiency curves showing the classification ability of the
\ac{CNN} as a function of distance for both mechanisms and networks.  The left
panel shows the results for the neutrino-driven mechanism, while the right
shows those for the magnetorotational mechanism. 
At a certain value of \ac{FAP} and a distance, the value of \ac{TAP}
will be plotted only if it is not zero.
In both panels, the solid
lines show the results for the network H+L+VK, and the dashed lines for HLVK.
Three \acp{FAP} values are chosen, blue for \ac{FAP} $=1\%$, green for \ac{FAP}
$=0.1\%$, red for \ac{FAP} $=0.01\%$.\label{fig:eff}}
\end{figure*}

%
% the TAP vs distance plot for fixed threshold
%
\begin{figure*}
     \begin{center}
        \subfigure[]{
            \label{fig:ROCfixed1}
            \includegraphics[width=0.475\textwidth]{ROC_fixed_neutrino.png}
        }\quad
        \subfigure[]{
            \label{fig:ROCfixed2}
            \includegraphics[width=0.475\textwidth]{ROC_fixed_mag.png}
        }
    \end{center}
    \caption{The ability of the \ac{CNN} in
distinguishing input data with a fixed decision threshold $(90\%)$, 
and their corresponding \acp{FAP} and \acp{TAP}. 
The left panel shows the results for the neutrino-driven mechanism.
Since for the neutrino-driven mechanism, the value of \ac{TAP} decreases to zero rapidly
as distance increases, only the distances at which the corresponding \acp{TAP} are not zero are plotted.
In the plot, stars are for the network H+L+VK, and the dots are for the network HLVK.
The right panel shows the results for the magnetorotational mechanism. 
In the right panel, the solid lines show the \acp{TAP} and \acp{FAP} 
for the network H+L+VK, and the
dashed lines show those for HLVK.\label{fig:ROCfixed}}
\end{figure*}
